Open Policing Project: Coverage Rates

### 2018-11-01 lib/bunching_report.Rmd
progress

```{r, echo = FALSE}
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
source("bunching_test.R")
```

@@

```{r ok, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("ok", "oklahoma city")
tbl <-
  tbl %>%
  mutate(
    age_group = as.integer(subject_age / 10),
    hour_of_day = hour(hms(time))
  )
bt <- bunching_test(tbl, division, hour_of_day, age_group, vehicle_make)
bt$results$plots$over
bt$results$plots$bunching
bt$results$plots$lenience
bt$results$plots$coefficient
```

@@

```{r dallas, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("tx", "dallas")
tbl <- mutate(tbl, hour_of_day = hour(hms(time)))
bt <- bunching_test(tbl, region, hour_of_day, vehicle_type)
bt$results$plots$over
bt$results$plots$bunching
bt$results$plots$lenience
bt$results$plots$coefficient
```
\newpage

@@

```{r plano, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("tx", "plano")
tbl <- mutate(tbl, hour_of_day = hour(hms(time)))
# NOTE: location is null 99.97% of the time where speed is defined
bt <- bunching_test(tbl, hour_of_day, vehicle_make)
bt$results$plots$over
bt$results$plots$bunching
bt$results$plots$lenience
bt$results$plots$coefficient
```

>>>>

```{r, echo = FALSE}
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
source("bunching_test.R")

over_limit <- 40

display <- function(bt) {
  print(bt$results$plots$over)
  print(bt$results$plots$bunching)
  print(bt$results$plots$lenience)
  print(bt$results$plots$over_by_demographic_and_lenience)
  print(bt$results$plots$difference)
  print(bt$results$plots$coefficient)
}
```

@@

```{r ok, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("ok", "oklahoma city")
tbl <-
  tbl %>%
  mutate(
    age_group = as.integer(subject_age / 10),
    hour_of_day = hour(hms(time))
  )
bt <- bunching_test(
  tbl,
  division,
  hour_of_day,
  age_group,
  vehicle_make,
  over_limit = over_limit
)
display(bt)
kable(bt$results$difference_in_difference)
```

@@

```{r dallas, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("tx", "dallas")
tbl <- mutate(tbl, hour_of_day = hour(hms(time)))
bt <- bunching_test(
  tbl,
  region,
  hour_of_day,
  vehicle_type,
  over_limit = over_limit
)
display(bt)
kable(bt$results$difference_in_difference)
```

@@

```{r plano, fig.height=3.75, fig.width=7}
tbl <- opp_load_data("tx", "plano")
tbl <- mutate(tbl, hour_of_day = hour(hms(time)))
# NOTE: location is null 99.97% of the time where speed is defined
bt <- bunching_test(
  tbl,
  hour_of_day,
  vehicle_make,
  over_limit = over_limit
)
display(bt)
kable(bt$results$difference_in_difference)
```
